---
title: "Winter Challenge"
author: "Michael He"
date: "9/20/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task 1
On Shopify, we have exactly 100 sneaker shops, and each of these shops sells only one model of shoe. We want to do some analysis of the average order value (AOV). When we look at orders data over a 30 day window, we naively calculate an AOV of $3145.13. Given that we know these shops are selling sneakers, a relatively affordable item, something seems wrong with our analysis. 

### Answers 1A
Think about what could be going wrong with our calculation. Think about a better way to evaluate this data. 

A quick glimpse of the dataset shows the bulk orders, which can significantly distort the average order value. In particular, shop 42 sells bulk orders worth 704,000 dollars to user 607. This is a big outlier we should filter from our AOV calculation. The new AOV is 754.1 dollars. 

Now we also want to look at the selling prices. Shop 78 sells very expensive sneakers worth 25,725 dollars a pair, and the next most expensive shoe costs 352 dollars, which is a lot less expensive. If we filter out shop 78 in addition to shop 42, then the new AOV is 302.6 dollars. 

```{r}
library(googlesheets4) 
library(tidyverse)

# downloading the spreadsheet completely
gs4_deauth()
sneakershop <- read_sheet("16i38oonuX1y1g7C_UAmiK9GkY7cS-64DfiDMNiR41LM",
sheet="Sheet1",)

# a quick ordering of order in descending dollar amount
sneakershop %>%
  arrange(desc(order_amount))

# filtering out the 700k orders 
sneakershop %>%
  filter(order_amount < 160000) %>%
  summarize(AOV = mean(order_amount))

# figure out which shoes are expensive per pair
sneakershop %>%
  mutate(price_level = order_amount / total_items) %>%
  filter(order_amount < 160000) %>%
  filter(price_level < 25725) %>%
  summarize(AOV = mean(order_amount))
```

### Part 1B & 1C

What metric would you report for this dataset? What is its value?

I would look at the median order amount, because it shows how much customers in the middle of the shopping spectrum spent. Here the median order amount is 284 dollars and the median total items bought is 2. This makes sense, as most online shoppers usually buy only a few pairs of sneakers at a time and sneaker prices generally fall within the low 3-digit range.

```{r}
sneakershop %>%
  summarize(MedOrd = median(order_amount), MedItem = median(total_items))
```

## Part 2

For this question you’ll need to use SQL. Follow this link to access the data set required for the challenge. Please use queries to answer the following questions. Paste your queries along with your final numerical answers below.

https://www.w3schools.com/SQL/TRYSQL.ASP?FILENAME=TRYSQL_SELECT_ALL

### Answer Part 2A 

How many orders were shipped by Speedy Express in total?


### Answer Part 2B

What is the last name of the employee with the most orders?


### Answer Part 2C

What product was ordered the most by customers in Germany?




